{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-29 paper/tex/sections/results.tex
move figures around into more sensible positions

\subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
In the top panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems. Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect. This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.

@@

\begin{figure}[thb]
    \centering
    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights. The coloured lines show the 75\% contour for each of the individual DCO types. The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
    \label{fig:detectable_distance_dist}
\end{figure}

@@

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
    \caption{Cumulative distribution function for error on the chirp mass. Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The shaded region indicates region with unmeasureable chirp mass.}
    \label{fig:m_c_unc}
\end{figure}

>>>>

\subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights. The coloured lines show the 75\% contour for each of the individual DCO types. The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
    \label{fig:detectable_distance_dist}
\end{figure}

In the top panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems. Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect. This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.

@@

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
    \caption{Cumulative distribution function for error on the chirp mass. Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). The shaded region indicates region with unmeasureable chirp mass.}
    \label{fig:m_c_unc}
\end{figure}

@@
